---
title: Short Paper
author:
  - name: Anson Main
    email: maina@missouri.edu
    affiliation: School of Natural Resources
    footnote: Corresponding Author
  - name: Elisabeth Webb
    email: webbli@missouri.edu
    affiliation: School of Natural Resources
address:
  - code: Some Institute of Technology
    address: Department, Street, City, State, Zip
  - code: Another University
    address: Department, Street, City, State, Zip
abstract: |
  This is the abstract.

  It consists of two paragraphs.

bibliography: mybibfile.bib
output: rticles::elsevier_article
---

```{r, message=FALSE, warning=FALSE, echo=FALSE}
Meta <- readRDS("Meta3.rds")
Meta <- dplyr::filter(Meta, Authors != "Tinsley et al.")

library(ggplot2)
library(metafor)
```

# Methods

All analysis were carried away with the R Statistical Software [@Rcore], all meta-analyses were made on the metafor package [@viechtbauer2010conducting]. Our estimations were based on the use of random/mixed-effects models form of meta-analyses, which provide an unconditional inference about a larger set of studies from which the k studies included in the meta-analysis are assumed to be a random sample [@hedges1998fixed]. This estimations do not assume that this larger set consists only of studies that have actually been conducted, but instead envision a hypothetical population of studies that comprises studies that have been conducted, that could have been conducted, or that may be conducted in the future [@hedges1998fixed].

We used the *escalc* function of the metafor package to estimate the effect size estimates  [@viechtbauer2010conducting], we used the *standardized mean difference with heteroscedastic population variances in the two groups* (SDMH) as our estimator for effect size [@bonett2009meta], the metafor package also corrects the slight positive bias of the estimation following [@Wasserman1988]. To be extra conservative we used the unbiased estimates of the sampling variances. In all cases the residual heterogeneity estimator was Hedges. 

Since we used mixed effect models we used the The Knapp and Hartung adjustment **(Knapp and Hartung, 2003)** to  test the individual coefficients of the model. 

## Test for (Residual) Heterogeneity

For each model we tested for residual heterogeneity, if we used models without moderators, then the Cochran's Q-test [@cochran1954combination] was used to test whether the variability in the observed effect sizes or outcomes is larger than would be expected based on sampling variability alone. *A significant test suggests that the true effects or outcomes are heterogeneous*. When moderators were included in the models the Q_E-test for residual heterogeneity was used, this tests whether the variability in the observed effect sizes or outcomes not accounted for by the moderators included in the model is larger than would be expected based on sampling variability alone. When using moderators to explain more variability a pseudo R squared was computed following [@raudenbush2009analyzing].


# Results

As we can see in figure 1, the most common type of performance measured in studies was abundance, with 101 estimations, followed by reproduction with 44 estimation, behavior with 23, and finally survival and condition with 16 each.

```{r, message=FALSE, warning=FALSE, echo=FALSE, fig.cap= "Number of estimation of effect size within the meta-analyses"}

ggplot(Meta, aes(x=reorder(Fitness.measure,Fitness.measure, function(x)-length(x)))) + geom_bar() + xlab("Performance measure") + ylab("Number of studies") + theme_classic()
```

```{r, message=FALSE, warning=FALSE, echo=FALSE}

library(metafor)

#Abundance
Abundance <- dplyr::filter(Meta, Fitness.measure == "abundance")


dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Abundance, vtype = "UB")

res <- rma(yi, vi, data=dat1, refline = 0, method = "HE", slab = paste(dat1$Authors, dat1$Year))

Abund <- data.frame(estimate = res$b, ci.ub = res$ci.ub, ci.lb = res$ci.lb, group = c("Abundance"), p = res$pval, n =nrow(Abundance), I2= res$I2, pvalCT = res$QEp)
#Behavior

Behavior <- dplyr::filter(Meta, Fitness.measure == "behavior")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Behavior, vtype = "UB")

res2 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", slab = paste(dat1$Authors, dat1$Year))

Behav <- data.frame(estimate = res2$b, ci.ub = res2$ci.ub, ci.lb = res2$ci.lb, group = c("Behavior"), p = res2$pval, n =nrow(Behavior), I2= res2$I2, pvalCT = res2$QEp)
#Survival

survival <- dplyr::filter(Meta, Fitness.measure == "survival")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=survival, vtype = "UB")

res3 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", slab = paste(dat1$Authors, dat1$Year))

Surviv <- data.frame(estimate = res3$b, ci.ub = res3$ci.ub, ci.lb = res3$ci.lb, group = c("Survival"), p = res3$pval, n =nrow(survival), I2= res3$I2, pvalCT = res3$QEp)

#Reproduction

reproduction <- dplyr::filter(Meta, Fitness.measure == "reproduction")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=reproduction, vtype = "UB")

res4 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", slab = paste(dat1$Authors, dat1$Year))

Reprod <- data.frame(estimate = res4$b, ci.ub = res4$ci.ub, ci.lb = res4$ci.lb, group = c("Reproduction"), p = res4$pval, n =nrow(reproduction), I2= res4$I2, pvalCT = res4$QEp)

#Condition

condition <- dplyr::filter(Meta, Fitness.measure == "condition")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=condition, vtype = "UB")

res5 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", slab = paste(dat1$Authors, dat1$Year))

Cond <- data.frame(estimate = res5$b, ci.ub = res5$ci.ub, ci.lb = res5$ci.lb, group = c("Condition"), p = res5$pval, n =nrow(condition), I2= res5$I2, pvalCT = res5$QEp)

All <- rbind(Abund, Behav, Surviv, Reprod, Cond)
knitr::kable(All, digits = 3, row.names = FALSE, caption = "effect size of the Standardized mean difference for each type of estimation of performance, it's standard error and p-value")
```

## Overall effect size

As we can see in table 1 and figure 2, all estimations of the effects are negative. However, only abundance, survival and condition have significative negative effects. Survival has the highest effect size, with a mean difference estimation of `r round(Surviv$estimate,2)`


```{r, message=FALSE, warning=FALSE, echo=FALSE, fig.cap= "effect size of the Standardized mean difference for each type of estimation of performance and it's standard error"}
All <- All[-4,]

ggplot(All, aes(x = group, y = estimate)) + geom_point(aes(size = n)) + coord_flip() + geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub),width=0.0) + geom_hline(yintercept = 0, linetype=2) + ylim(c(-14, 14)) + ylab(c("Standardized Mean Difference")) + theme_classic() + xlab(c(""))

```

# Estimations using moderators:

# Abundance


```{r, message=FALSE, warning=FALSE, echo=FALSE}

### Abundance and functional group

Abundance <- dplyr::filter(Meta, Fitness.measure == "abundance")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Abundance, vtype = "UB")

res <- rma(yi, vi, data=dat1, refline = 0, method = "HE", slab = paste(dat1$Authors, dat1$Year))

model0 <- data.frame(model = "y ~ 1", p_value = res$QMp, R_squared = 0, AICc = res$fit.stats$ML[5])

nullmod <- data.frame(estimate = res$b, ci.ub = res$ci.ub, ci.lb = res$ci.lb, group = c("Null"), p = res$pval, n =nrow(Abundance))



res0 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  factor(Functional.group) - 1, slab = paste(dat1$Authors, dat1$Year))

functionalgroup <- data.frame(estimate = res0$b, ci.ub = res0$ci.ub, ci.lb = res0$ci.lb, group = c("detritivore","mixed", "omnivore", "pollinator", "predator"), p = res0$pval, n = c(length(dplyr::filter(Abundance, Functional.group == "detritivore")$Functional.group),length(dplyr::filter(Abundance, Functional.group == "mixed")$Functional.group), length(dplyr::filter(Abundance, Functional.group == "omnivore")$Functional.group), length(dplyr::filter(Abundance, Functional.group == "pollinator")$Functional.group), length(dplyr::filter(Abundance, Functional.group == "predator")$Functional.group)))

res1 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  factor(Functional.group), slab = paste(dat1$Authors, dat1$Year))

model1 <- data.frame(model = "y ~ Functional group", p_value = res1$QMp, R_squared = round(res1$R2/100,2), AICc = res1$fit.stats$ML[5])

```




```{r, message=FALSE, warning=FALSE, echo=FALSE}
### Abundance and nesting area


Abundance <- dplyr::filter(Meta, Fitness.measure == "abundance")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Abundance, vtype = "UB")

res <- rma(yi, vi, data=dat1, refline = 0, method = "HE", slab = paste(dat1$Authors, dat1$Year))

nullmod <- data.frame(estimate = res$b, ci.ub = res$ci.ub, ci.lb = res$ci.lb, group = c("Null"), p = res$pval, n =nrow(Abundance))



res0 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  factor(Nesting.Area) - 1, slab = paste(dat1$Authors, dat1$Year))

NestingArea <- data.frame(estimate = res0$b, ci.ub = res0$ci.ub, ci.lb = res0$ci.lb, group = c("aboveground","both", "ground"), p = res0$pval, n = c(length(dplyr::filter(Abundance, Functional.group == "aboveground")$Nesting.Area),length(dplyr::filter(Abundance, Functional.group == "both")$Nesting.Area), length(dplyr::filter(Abundance, Functional.group == "ground")$Nesting.Area)))

res4 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  factor(Nesting.Area), slab = paste(dat1$Authors, dat1$Year))

model4 <- data.frame(model = "y ~ Nesting Area", p_value = res4$QMp, R_squared = round(res4$R2/100,2), AICc = res4$fit.stats$ML[5])

```




```{r, message=FALSE, warning=FALSE, echo=FALSE}
### Abundance and concentration (Kg/Ha) for Powder/granular treatment

Abundance <- dplyr::filter(Meta, Fitness.measure == "abundance")

Abundance_kg_ha <- dplyr::filter(Abundance, Application.Units == "kg/ha")
Abundance_kg_ha <- dplyr::filter(Abundance_kg_ha, TreatmentType == "powder/granular")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Abundance_kg_ha, vtype = "UB")

res7 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  AI.Rate_T1, slab = paste(dat1$Authors, dat1$Year))

preds <- predict(res7, newmods = cbind(seq(from = min(dat1$AI.Rate_T1), to = max(dat1$AI.Rate_T1), length.out =  20)), addx = TRUE)
preds <- data.frame(pred = preds$pred, ci.lb = preds$ci.lb, ci.ub = preds$ci.ub, X.AI.Rate_T1 = preds$X[,2])

model7 <- data.frame(model = "y ~ Concentration [Kg/Ha]", p_value = res7$QMp, R_squared = round(res7$R2/100,2), AICc = res7$fit.stats$ML[5])
```

```{r, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.cap= "effect size of the Standardized mean difference of behavior and concentration (Kg/Ha) for powder/granular aplications"}

ggplot(dat1, aes(x = AI.Rate_T1, y = yi))  + geom_ribbon(data = preds, aes(x = X.AI.Rate_T1, y = pred, ymin = ci.lb, ymax = ci.ub), fill = "grey", alpha = 0.5) + theme_classic() + geom_line(data = preds, aes(x = X.AI.Rate_T1, y = pred)) + geom_point(aes(size = Study.T1..n.)) + xlab("Concentration (Kg/Ha)") + ylab("Standardized mean difference") + geom_hline(yintercept = 0, lty= 2) + scale_size("Number of studies") + scale_x_continuous(labels = scales::comma)

```


```{r, message=FALSE, warning=FALSE, echo=FALSE}
### Abundance and concentration (g/Kg) for seed treatment

Abundance <- dplyr::filter(Meta, Fitness.measure == "abundance")

Abundance_g_kg <- dplyr::filter(Abundance, Application.Units == "g/kg")


dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Abundance_g_kg, vtype = "UB")

res8 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  AI.Rate_T1, slab = paste(dat1$Authors, dat1$Year))

preds <- predict(res8, newmods = cbind(seq(from = min(dat1$AI.Rate_T1), to = max(dat1$AI.Rate_T1), length.out =  20)), addx = TRUE)
preds <- data.frame(pred = preds$pred, ci.lb = preds$ci.lb, ci.ub = preds$ci.ub, X.AI.Rate_T1 = preds$X[,2])

model8 <- data.frame(model = "y ~ Concentration [g/kg]", p_value = res8$QMp, R_squared = round(res8$R2/100,2), AICc = res8$fit.stats$ML[5])
```


```{r, message=FALSE, warning=FALSE, echo=FALSE}
### Abundance concentration [g/Kg] and functional group

Abundance <- dplyr::filter(Meta, Fitness.measure == "abundance")
Abundance <- dplyr::filter(Meta, Fitness.measure == "abundance")

Abundance_g_kg <- dplyr::filter(Abundance, Application.Units == "g/kg")


dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Abundance_g_kg, vtype = "UB")

res9 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  AI.Rate_T1+ factor(Functional.group), slab = paste(dat1$Authors, dat1$Year))

library(caret)

#newmods = expand.grid(AI.Rate_T1 = seq(from = min(dat1$AI.Rate_T1), to = max(dat1$AI.Rate_T1), length.out =  20), Functional.group = c("mixed", "pollinator","predator"))

newmods = expand.grid(AI.Rate_T1 = seq(from = min(dat1$AI.Rate_T1), to = max(dat1$AI.Rate_T1), length.out =  20), Functional.group = c("mixed","predator"))

dum <- dummyVars(~ Functional.group, data = newmods)

NM <- cbind(newmods[,1],predict(dum, newmods))

#preds <- predict(res9, newmods = NM[,1:3], addx = TRUE)

preds <- predict(res9, newmods = NM[,1:2], addx = TRUE)


preds <- data.frame(pred = preds$pred, ci.lb = preds$ci.lb, ci.ub = preds$ci.ub, X.AI.Rate_T1 = preds$X[,2], Functional.group = newmods$Functional.group)

model9 <- data.frame(model = "y ~ Concentration [g/kg] + Functional group", p_value = res9$QMp, R_squared = round(res9$R2/100,2), AICc = res9$fit.stats$ML[5])

```

```{r, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.cap= "effect size of the Standardized mean difference of Abundance and concentration [g/Kg]"}

ggplot(dat1, aes(x = AI.Rate_T1, y = yi))  + geom_ribbon(data = preds, aes(x = X.AI.Rate_T1, y = pred, ymin = ci.lb, ymax = ci.ub, fill = Functional.group), alpha = 0.5) + theme_classic() + geom_line(data = preds, aes(x = X.AI.Rate_T1, y = pred, lty = Functional.group)) + geom_point() + xlab("Concentration [g/kg]") + ylab("Standardized mean difference") + geom_hline(yintercept = 0, lty= 2) + scale_fill_grey("Functional Group") + scale_linetype(name = "Functional Group")

```


```{r, message=FALSE, warning=FALSE, echo=FALSE}
### Abundance concentration [g/Kg] and nesting area

Abundance <- dplyr::filter(Meta, Fitness.measure == "abundance")
Abundance <- dplyr::filter(Meta, Fitness.measure == "abundance")

Abundance_g_kg <- dplyr::filter(Abundance, Application.Units == "g/kg")


dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Abundance_g_kg, vtype = "UB")

res10 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  AI.Rate_T1+ factor(Nesting.Area), slab = paste(dat1$Authors, dat1$Year))

library(caret)

newmods = expand.grid(T1_ppb = seq(from = min(dat1$AI.Rate_T1), to = max(dat1$AI.Rate_T1), length.out =  20), Nesting.Area = c("aboveground", "both"))

dum <- dummyVars(~ Nesting.Area, data = newmods)

NM <- cbind(newmods[,1],predict(dum, newmods))

preds <- predict(res10, newmods = NM[,1:2], addx = TRUE)

preds <- data.frame(pred = preds$pred, ci.lb = preds$ci.lb, ci.ub = preds$ci.ub, X.AI.Rate_T1 = preds$X[,2])

model10 <- data.frame(model = "y ~ Concentration [g/kg] + Nesting Area", p_value = res10$QMp, R_squared = round(res10$R2/100,2), AICc = res10$fit.stats$ML[5])

```


```{r, message=FALSE, warning=FALSE, echo=FALSE}
### Abundance concentration [g/Kg] and nesting area

Abundance <- dplyr::filter(Meta, Fitness.measure == "abundance")
Abundance <- dplyr::filter(Meta, Fitness.measure == "abundance")

Abundance_g_kg <- dplyr::filter(Abundance, Application.Units == "g/kg")


dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Abundance_g_kg, vtype = "UB")

res11 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  AI.Rate_T1+ factor(Nesting.Area) + factor(Functional.group), slab = paste(dat1$Authors, dat1$Year))

model11 <- data.frame(model = "y ~ Concentration [g/kg] + Nesting Area + Functional Group", p_value = res11$QMp, R_squared = round(res11$R2/100,2), AICc = res11$fit.stats$ML[5])

```


```{r, message=FALSE, warning=FALSE, echo=FALSE}
### Abundance concentration [kg/ha] and nesting area

Abundance_kg_ha <- dplyr::filter(Abundance, Application.Units == "kg/ha")
Abundance_kg_ha <- dplyr::filter(Abundance_kg_ha, TreatmentType == "powder/granular")


dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Abundance_kg_ha, vtype = "UB")

res12 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  AI.Rate_T1+ factor(Nesting.Area) + factor(Functional.group), slab = paste(dat1$Authors, dat1$Year))

model12 <- data.frame(model = "y ~ Concentration [kg/ha] + Nesting Area + Functional Group", p_value = res12$QMp, R_squared = round(res12$R2/100,2), AICc = res12$fit.stats$ML[5])

```

```{r, message=FALSE, warning=FALSE, echo=FALSE}
### Abundance and nesting area


Abundance <- dplyr::filter(Meta, Fitness.measure == "abundance")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Abundance, vtype = "UB")

res13 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  factor(Order) + factor(Functional.group), slab = paste(dat1$Authors, dat1$Year))

model13 <- data.frame(model = "y ~ Order + Functional group", p_value = res13$QMp, R_squared = round(res13$R2/100,2), AICc = res13$fit.stats$ML[5])

```

### Comparison of models

```{r, echo= FALSE}
All <- rbind(model0, model1, model4, model7, model8, model9, model10, model11, model12, model13)

All <- dplyr::arrange(All, AICc)

All$deltaAICc <- (All$AICc - min(All$AICc))

SUMDELTA <- sum(exp(-0.5*All$deltaAICc))

All$Weight <- exp(-0.5*All$deltaAICc)/SUMDELTA

knitr::kable(All, digits = 3, row.names = FALSE, caption = "Comparison of models taking into account p value, Pseudo R squared and AICc")
```



# Behaviour



```{r, message=FALSE, warning=FALSE, echo=FALSE}
### Behaviour and AI type

Behavior <- dplyr::filter(Meta, Fitness.measure == "behavior")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Behavior, vtype = "UB")

res <- rma(yi, vi, data=dat1, refline = 0, method = "HE", slab = paste(dat1$Authors, dat1$Year))

nullmod <- data.frame(estimate = res$b, ci.ub = res$ci.ub, ci.lb = res$ci.lb, group = c("Null"), p = res$pval, n =nrow(Behavior))



res0 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  factor(TreatmentType) - 1, slab = paste(dat1$Authors, dat1$Year))

AItype <- data.frame(estimate = res0$b, ci.ub = res0$ci.ub, ci.lb = res0$ci.lb, group = c("commercial","granular", "not specified", "seed treatment", "solution", "technical grade"), p = res0$pval, n = c(NROW(dplyr::filter(Behavior, TreatmentType == "commercial")), NROW(dplyr::filter(Behavior, TreatmentType == "granular")), NROW(dplyr::filter(Behavior, TreatmentType == "not specified")), NROW(dplyr::filter(Behavior, TreatmentType == "seed treatment")), NROW(dplyr::filter(Behavior, TreatmentType == "solution")), NROW(dplyr::filter(Behavior, TreatmentType == "technical grade"))))

All <- rbind(nullmod, AItype)

res1 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  factor(TreatmentType), slab = paste(dat1$Authors, dat1$Year))

model1 <- data.frame(model = "y ~ Treatment type", p_value = res1$QMp, R_squared = round(res1$R2/100,2), AICc = res1$fit.stats$ML[5])

```


```{r, message=FALSE, warning=FALSE, echo=FALSE}
Behavior <- dplyr::filter(Meta, Fitness.measure == "behavior")
Behavior_ppb <- Behavior[!is.na(Behavior$T1_ppb),]

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Behavior_ppb, vtype = "UB")

res2 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  T1_ppb, slab = paste(dat1$Authors, dat1$Year))

#res2 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  T1_ppb +  factor(Functional.group), slab = paste(dat1$Authors, dat1$Year))
preds <- predict(res2, newmods = cbind(seq(from = min(dat1$T1_ppb), to = max(dat1$T1_ppb), length.out =  20)), addx = TRUE)
preds <- data.frame(pred = preds$pred, ci.lb = preds$ci.lb, ci.ub = preds$ci.ub, X.T1_ppb = preds$X[,2])

model2 <- data.frame(model = "y ~ Concentration [ppb]", p_value = res2$QMp, R_squared = round(res2$R2/100,2), AICc = res2$fit.stats$ML[5])
```



```{r, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.cap= "effect size of the Standardized mean difference of behavior and concentration (ppb)"}

ggplot(dat1, aes(x = T1_ppb, y = yi))  + geom_ribbon(data = preds, aes(x = X.T1_ppb, y = pred, ymin = ci.lb, ymax = ci.ub), fill = "grey", alpha = 0.5) + theme_classic() + geom_line(data = preds, aes(x = X.T1_ppb, y = pred)) + geom_point(aes(size = Study.T1..n.)) + xlab("Concentration (ppb)") + ylab("Standardized mean difference") + geom_hline(yintercept = 0, lty= 2) + scale_size("Number of studies") + scale_x_continuous(labels = scales::comma)

```


```{r, message=FALSE, warning=FALSE, echo=FALSE}
### Behavior, concentration and neonic type

Behavior <- dplyr::filter(Meta, Fitness.measure == "behavior")
Behavior_ppb <- Behavior[!is.na(Behavior$T1_ppb),]

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Behavior_ppb, vtype = "UB")


res3 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  T1_ppb + factor(Treatment.2), slab = paste(dat1$Authors, dat1$Year))

library(caret)

newmods = expand.grid(T1_ppb = seq(from = min(dat1$T1_ppb), to = max(dat1$T1_ppb), length.out =  20), Treatment.2 = c("IMI", "THX"))

dum <- dummyVars(~ Treatment.2, data = newmods)

NM <- cbind(newmods[,1],predict(dum, newmods))

preds <- predict(res3, newmods = NM[,1:2])

preds <- data.frame(pred = preds$pred, ci.lb = preds$ci.lb, ci.ub = preds$ci.ub, T1_ppb = newmods$T1_ppb, Treatment.2 = newmods$Treatment.2)

model3 <- data.frame(model = "y ~ Concentration + neonic type", p_value = res3$QMp, R_squared = round(res3$R2/100,2), AICc = res3$fit.stats$ML[5])
```


```{r, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.cap= "effect size of the concentration and neonic type on the behavior Standardized mean difference of abundance"}

ggplot(preds, aes(x = T1_ppb, y = pred))  + geom_ribbon(alpha = 0.5,aes(ymin = ci.lb, ymax = ci.ub, fill = Treatment.2)) + theme_classic() + geom_line(aes(lty = Treatment.2))+ xlab("Concentration (ppb)") + ylab("Standardized mean difference") + geom_hline(yintercept = 0, lty= 2) + scale_fill_grey(name = "Neonic Type") + geom_point(alpha = 0.8, data= dat1, aes(x = T1_ppb, y = yi, size = Study.T1..n., color = Treatment.2)) + scale_color_grey(name = "Neonic Type") + scale_linetype(name = "Neonic Type") + scale_size(name = "number of studies") + scale_x_continuous(labels = scales::comma)
```

```{r, message=FALSE, warning=FALSE, echo=FALSE}
### Behaviorand neonic type

Behavior <- dplyr::filter(Meta, Fitness.measure == "behavior")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Behavior, vtype = "UB")


res4 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~ factor(Treatment.2), slab = paste(dat1$Authors, dat1$Year))

model4 <- data.frame(model = "y ~ neonic type", p_value = res4$QMp, R_squared = round(res4$R2/100,2), AICc = res4$fit.stats$ML[5])
```

```{r, message=FALSE, warning=FALSE, echo=FALSE}
### Behaviorand study type

Behavior <- dplyr::filter(Meta, Fitness.measure == "behavior")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Behavior, vtype = "UB")


res5 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~ factor(Study.Type), slab = paste(dat1$Authors, dat1$Year))

model5 <- data.frame(model = "y ~ study type", p_value = res5$QMp, R_squared = round(res5$R2/100,2), AICc = res5$fit.stats$ML[5])
```

```{r, message=FALSE, warning=FALSE, echo=FALSE}
### Behaviorand Ai type and functional group

Behavior <- dplyr::filter(Meta, Fitness.measure == "behavior")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Behavior, vtype = "UB")


res6 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~ factor(Functional.group) + factor(TreatmentType), slab = paste(dat1$Authors, dat1$Year))

model6 <- data.frame(model = "y ~ Treatment type + Functional group", p_value = res6$QMp, R_squared = round(res6$R2/100,2), AICc = res6$fit.stats$ML[5])
```

### Comparison of models

```{r, echo= FALSE}
All <- rbind(model1, model2, model3, model4, model5, model6)

All <- dplyr::arrange(All, AICc)

All$deltaAICc <- (All$AICc - min(All$AICc))

SUMDELTA <- sum(exp(-0.5*All$deltaAICc))

All$Weight <- exp(-0.5*All$deltaAICc)/SUMDELTA

knitr::kable(All, digits = 3, row.names = FALSE, caption = "Comparison of models taking into account p value, Pseudo R squared and AICc")
```

#Reproduction

```{r, message=FALSE, warning=FALSE, echo=FALSE}
### Reproduction, functional group and Order

Reproduction <- dplyr::filter(Meta, Fitness.measure == "reproduction")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Reproduction, vtype = "UB")


res1 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~ factor(Functional.group) + factor(Order), slab = paste(dat1$Authors, dat1$Year))

model1 <- data.frame(model = "y ~ Order + Functional group", p_value = res1$QMp, R_squared = round(res1$R2/100,2), AICc = res1$fit.stats$ML[5])
```

```{r, message=FALSE, warning=FALSE, echo=FALSE}
### Reproduction, Nesting area

Reproduction <- dplyr::filter(Meta, Fitness.measure == "reproduction")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Reproduction, vtype = "UB")


res2 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~ factor(Nesting.Area), slab = paste(dat1$Authors, dat1$Year))


model2 <- data.frame(model = "y ~ Order + Nesting Area", p_value = res2$QMp, R_squared = round(res2$R2/100,2), AICc = res2$fit.stats$ML[5])
```

```{r, message=FALSE, warning=FALSE, echo=FALSE}
#Reproduction and ppb
Reproduction <- dplyr::filter(Meta, Fitness.measure == "reproduction")
Reproduction_ppb <- Reproduction[!is.na(Reproduction$T1_ppb),]

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Reproduction_ppb, vtype = "UB")

res3 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  T1_ppb, slab = paste(dat1$Authors, dat1$Year))


model3 <- data.frame(model = "y ~ Concentration [ppb]", p_value = res3$QMp, R_squared = round(res3$R2/100,2), AICc = res3$fit.stats$ML[5])
```

```{r, message=FALSE, warning=FALSE, echo=FALSE}
#Reproduction, ppb and Neonic type
Reproduction <- dplyr::filter(Meta, Fitness.measure == "reproduction")
Reproduction_ppb <- Reproduction[!is.na(Reproduction$T1_ppb),]

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Reproduction_ppb, vtype = "UB")

res4 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  T1_ppb + Treatment.2, slab = paste(dat1$Authors, dat1$Year))


library(caret)

newmods = expand.grid(T1_ppb = seq(from = min(dat1$T1_ppb), to = max(dat1$T1_ppb), length.out =  20), Treatment.2 = c("CLO", "IMI", "THX"))

dum <- dummyVars(~ Treatment.2, data = newmods)

NM <- cbind(newmods[,1],predict(dum, newmods))

preds <- predict(res4, newmods = NM[,1:3])

preds <- data.frame(pred = preds$pred, ci.lb = preds$ci.lb, ci.ub = preds$ci.ub, T1_ppb = newmods$T1_ppb, Treatment.2 = newmods$Treatment.2)

model4 <- data.frame(model = "y ~ Concentration [ppb] + Neonic type", p_value = res4$QMp, R_squared = round(res4$R2/100,2), AICc = res4$fit.stats$ML[5])
```

```{r, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.cap= "effect size of the concentration and neonic type on the reporoduction Standardized mean difference of abundance"}

ggplot(preds, aes(x = T1_ppb, y = pred))  + geom_ribbon(alpha = 0.5,aes(ymin = ci.lb, ymax = ci.ub, fill = Treatment.2)) + theme_classic() + geom_line(aes(lty = Treatment.2))+ xlab("Concentration (ppb)") + ylab("Standardized mean difference") + geom_hline(yintercept = 0, lty= 2) + scale_fill_grey(name = "Neonic Type") + geom_point(alpha = 0.8, data= dat1, aes(x = T1_ppb, y = yi, size = Study.T1..n., color = Treatment.2)) + scale_color_grey(name = "Neonic Type") + scale_linetype(name = "Neonic Type") + scale_size(name = "number of studies") + scale_x_continuous(labels = scales::comma)
```

### Comparison of models

```{r, echo= FALSE}
All <- rbind(model1, model2, model3, model4)

All <- dplyr::arrange(All, AICc)

All$deltaAICc <- (All$AICc - min(All$AICc))

SUMDELTA <- sum(exp(-0.5*All$deltaAICc))

All$Weight <- exp(-0.5*All$deltaAICc)/SUMDELTA

knitr::kable(All, digits = 3, row.names = FALSE, caption = "Comparison of models taking into account p value, Pseudo R squared and AICc")
```


References {#references .unnumbered}
==========
