---
title: Short Paper
author:
  - name: Anson Main
    email: maina@missouri.edu
    affiliation: School of Natural Resources
    footnote: Corresponding Author
  - name: Elisabeth Webb
    email: webbli@missouri.edu
    affiliation: School of Natural Resources
address:
  - code: Some Institute of Technology
    address: Department, Street, City, State, Zip
  - code: Another University
    address: Department, Street, City, State, Zip
abstract: |
  This is the abstract.

  It consists of two paragraphs.

bibliography: mybibfile.bib
output: rticles::elsevier_article
---

```{r, message=FALSE, warning=FALSE, echo=FALSE}
Meta <- readRDS("Meta.rds")

library(ggplot2)
library(metafor)
```

# Methods

All analysis were carried away with the R Statistical Software [@Rcore], all meta-analyses were made on the metafor package [@viechtbauer2010conducting]. Our estimations were based on the use of random/mixed-effects models form of meta-analyses, which provide an unconditional inference about a larger set of studies from which the k studies included in the meta-analysis are assumed to be a random sample [@hedges1998fixed]. This estimations do not assume that this larger set consists only of studies that have actually been conducted, but instead envision a hypothetical population of studies that comprises studies that have been conducted, that could have been conducted, or that may be conducted in the future [@hedges1998fixed].

We used the *escalc* function of the metafor package to estimate the effect size estimates  [@viechtbauer2010conducting], we used the *standardized mean difference with heteroscedastic population variances in the two groups* (SDMH) as our estimator for effect size [@bonett2009meta], the metafor package also corrects the slight positive bias of the estimation following [@Wasserman1988]. To be extra conservative we used the unbiased estimates of the sampling variances. In all cases the residual heterogeneity estimator was Hedges. 

Since we used mixed effect models we used the The Knapp and Hartung adjustment **(Knapp and Hartung, 2003)** to  test the individual coefficients of the model. 

## Test for (Residual) Heterogeneity

For each model we tested for residual heterogeneity, if we used models without moderators, then the Cochran's Q-test [@cochran1954combination] was used to test whether the variability in the observed effect sizes or outcomes is larger than would be expected based on sampling variability alone. *A significant test suggests that the true effects or outcomes are heterogeneous*. When moderators were included in the models the Q_E-test for residual heterogeneity was used, this tests whether the variability in the observed effect sizes or outcomes not accounted for by the moderators included in the model is larger than would be expected based on sampling variability alone. When using moderators to explain more variability a pseudo R squared was computed following [@raudenbush2009analyzing].


# Results

As we can see in figure 1, the most common type of performance measured in studies was abundance, with 101 estimations, followed by reproduction with 44 estimation, behavior with 23, and finally survival and condition with 16 each.

```{r, message=FALSE, warning=FALSE, echo=FALSE, fig.cap= "Number of estimation of effect size within the meta-analyses"}

ggplot(Meta, aes(x=reorder(Fitness.measure,Fitness.measure, function(x)-length(x)))) + geom_bar() + xlab("Performance measure") + ylab("Number of studies") + theme_classic()
```

```{r, message=FALSE, warning=FALSE, echo=FALSE}

library(metafor)

#Abundance
Abundance <- dplyr::filter(Meta, Fitness.measure == "abundance")


dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Abundance, vtype = "UB")

res <- rma(yi, vi, data=dat1, refline = 0, method = "HE", slab = paste(dat1$Authors, dat1$Year))

Abund <- data.frame(estimate = res$b, ci.ub = res$ci.ub, ci.lb = res$ci.lb, group = c("Abundance"), p = res$pval, n =nrow(Abundance), I2= res$I2, pvalCT = res$QEp)
#Behavior

Behavior <- dplyr::filter(Meta, Fitness.measure == "behavior")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Behavior, vtype = "UB")

res2 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", slab = paste(dat1$Authors, dat1$Year))

Behav <- data.frame(estimate = res2$b, ci.ub = res2$ci.ub, ci.lb = res2$ci.lb, group = c("Behavior"), p = res2$pval, n =nrow(Behavior), I2= res2$I2, pvalCT = res2$QEp)
#Survival

survival <- dplyr::filter(Meta, Fitness.measure == "survival")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=survival, vtype = "UB")

res3 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", slab = paste(dat1$Authors, dat1$Year))

Surviv <- data.frame(estimate = res3$b, ci.ub = res3$ci.ub, ci.lb = res3$ci.lb, group = c("Survival"), p = res3$pval, n =nrow(survival), I2= res3$I2, pvalCT = res3$QEp)

#Reproduction

reproduction <- dplyr::filter(Meta, Fitness.measure == "reproduction")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=reproduction, vtype = "UB")

res4 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", slab = paste(dat1$Authors, dat1$Year))

Reprod <- data.frame(estimate = res4$b, ci.ub = res4$ci.ub, ci.lb = res4$ci.lb, group = c("Reproduction"), p = res4$pval, n =nrow(reproduction), I2= res4$I2, pvalCT = res4$QEp)

#Condition

condition <- dplyr::filter(Meta, Fitness.measure == "condition")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=condition, vtype = "UB")

res5 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", slab = paste(dat1$Authors, dat1$Year))

Cond <- data.frame(estimate = res5$b, ci.ub = res5$ci.ub, ci.lb = res5$ci.lb, group = c("Condition"), p = res5$pval, n =nrow(condition), I2= res5$I2, pvalCT = res5$QEp)

All <- rbind(Abund, Behav, Surviv, Reprod, Cond)
knitr::kable(All, digits = 3, row.names = FALSE, caption = "effect size of the Standardized mean difference for each type of estimation of performance, it's standard error and p-value")
```

## Overall effect size

As we can see in table 1 and figure 2, all estimations of the effects are negative. However, only abundance, survival and condition have significative negative effects. Survival has the highest effect size, with a mean difference estimation of `r round(Surviv$estimate,2)`


```{r, message=FALSE, warning=FALSE, echo=FALSE, fig.cap= "effect size of the Standardized mean difference for each type of estimation of performance and it's standard error"}
All <- All[-4,]

ggplot(All, aes(x = group, y = estimate)) + geom_point(aes(size = n)) + coord_flip() + geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub),width=0.0) + geom_hline(yintercept = 0, linetype=2) + ylim(c(-10, 10)) + ylab(c("Standardized Mean Difference")) + theme_classic() + xlab(c(""))

```

# Estimations using moderators:

# Abundance

### Abundance and functional group

Using functional group as a moderator yields the following results

```{r, message=FALSE, warning=FALSE, echo=FALSE}
Abundance <- dplyr::filter(Meta, Fitness.measure == "abundance")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Abundance, vtype = "UB")

res <- rma(yi, vi, data=dat1, refline = 0, method = "HE", slab = paste(dat1$Authors, dat1$Year))

model0 <- data.frame(model = "y ~ 1", p_value = res$QMp, R_squared = 0, AICc = res$fit.stats$ML[5])

nullmod <- data.frame(estimate = res$b, ci.ub = res$ci.ub, ci.lb = res$ci.lb, group = c("Null"), p = res$pval, n =nrow(Abundance))



res0 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  factor(Functional.group) - 1, slab = paste(dat1$Authors, dat1$Year))

functionalgroup <- data.frame(estimate = res0$b, ci.ub = res0$ci.ub, ci.lb = res0$ci.lb, group = c("detritivore","mixed", "omnivore", "pollinator", "predator"), p = res0$pval, n = c(length(dplyr::filter(Abundance, Functional.group == "detritivore")$Functional.group),length(dplyr::filter(Abundance, Functional.group == "mixed")$Functional.group), length(dplyr::filter(Abundance, Functional.group == "omnivore")$Functional.group), length(dplyr::filter(Abundance, Functional.group == "pollinator")$Functional.group), length(dplyr::filter(Abundance, Functional.group == "predator")$Functional.group)))


All <- rbind(nullmod, functionalgroup)

knitr::kable(All, digits = 3, row.names = FALSE, caption = "effect size of the Standardized mean difference of abundance for each functional group and it's standard error")

res1 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  factor(Functional.group), slab = paste(dat1$Authors, dat1$Year))

model1 <- data.frame(model = "y ~ Functional group", p_value = res1$QMp, R_squared = round(res1$R2/100,2), AICc = res1$fit.stats$ML[5])

```

the the psuedo R squared for this model was `r round(res1$R2/100,2)`, that is despite the mixed and omnivore funtional groups being statistically significant, functional group on its own does not explain the variability of the results very well.

```{r, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.cap= "effect size of the Standardized mean difference of abundance for each functional group and it's standard error"}

ggplot(All, aes(x = group, y = estimate)) + geom_point(aes(size = n)) + coord_flip() + geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub),width=0.0) + geom_hline(yintercept = 0, linetype=2) + ylim(c(-7, 7)) + ylab(c("Standardized Mean Difference")) + theme_classic() + xlab(c(""))

```

### Abundance and nesting area

```{r, message=FALSE, warning=FALSE, echo=FALSE}
Abundance <- dplyr::filter(Meta, Fitness.measure == "abundance")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Abundance, vtype = "UB")

res <- rma(yi, vi, data=dat1, refline = 0, method = "HE", slab = paste(dat1$Authors, dat1$Year))

nullmod <- data.frame(estimate = res$b, ci.ub = res$ci.ub, ci.lb = res$ci.lb, group = c("Null"), p = res$pval, n =nrow(Abundance))



res0 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  factor(Nesting.Area) - 1, slab = paste(dat1$Authors, dat1$Year))

NestingArea <- data.frame(estimate = res0$b, ci.ub = res0$ci.ub, ci.lb = res0$ci.lb, group = c("aboveground","both", "ground"), p = res0$pval, n = c(length(dplyr::filter(Abundance, Functional.group == "aboveground")$Nesting.Area),length(dplyr::filter(Abundance, Functional.group == "both")$Nesting.Area), length(dplyr::filter(Abundance, Functional.group == "ground")$Nesting.Area)))


All <- rbind(nullmod, NestingArea)

knitr::kable(All, digits = 3, row.names = FALSE, caption = "effect size of the Standardized mean difference of abundance controling for nesting area and it's standard error")

res4 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  factor(Nesting.Area), slab = paste(dat1$Authors, dat1$Year))

model4 <- data.frame(model = "y ~ Nesting Area", p_value = res4$QMp, R_squared = round(res4$R2/100,2), AICc = res4$fit.stats$ML[5])

```

the the psuedo R squared for using nesting area as the only moderator was `r round(res4$R2/100,2)`, this model does not explain much.

### Abundance and concentration (ppb)

When we use concentration as parts per billion, the number of effect sizes diminishes from 101 to only nine.

```{r, message=FALSE, warning=FALSE, echo=FALSE}
Abundance <- dplyr::filter(Meta, Fitness.measure == "abundance")
Abundance <- Abundance[!is.na(Abundance$T1_ppb),]

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Abundance, vtype = "UB")

res2 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  T1_ppb, slab = paste(dat1$Authors, dat1$Year))

#res2 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  T1_ppb +  factor(Functional.group), slab = paste(dat1$Authors, dat1$Year))
preds <- predict(res2, newmods = cbind(seq(from = min(dat1$T1_ppb), to = max(dat1$T1_ppb), length.out =  20)), addx = TRUE)
preds <- data.frame(pred = preds$pred, ci.lb = preds$ci.lb, ci.ub = preds$ci.ub, X.T1_ppb = preds$X[,2])

model2 <- data.frame(model = "y ~ Concentration", p_value = res2$QMp, R_squared = round(res2$R2/100,2), AICc = res2$fit.stats$ML[5])
```

Despite that, the r squared of this model is `r round(res2$R2/100,2)`, that is over 40 percent of cariability explained by this factor alone. The relationship between concentration and Abundance can be seen in figure 4.


```{r, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.cap= "effect size of the Standardized mean difference of abundance and concentration (ppb)"}

ggplot(dat1, aes(x = T1_ppb, y = yi))  + geom_ribbon(data = preds, aes(x = X.T1_ppb, y = pred, ymin = ci.lb, ymax = ci.ub), fill = "grey", alpha = 0.5) + theme_classic() + geom_line(data = preds, aes(x = X.T1_ppb, y = pred)) + geom_point() + xlab("Concentration (ppb)") + ylab("Standardized mean difference") + geom_hline(yintercept = 0, lty= 2)

```

### Abundance and concentration (Kg/Ha) for Powder/granular treatment

When we use concentration as parts per billion, the number of effect sizes diminishes from 101 to only nine.

```{r, message=FALSE, warning=FALSE, echo=FALSE}
Abundance <- dplyr::filter(Meta, Fitness.measure == "abundance")

Abundance_kg_ha <- dplyr::filter(Abundance, Application.Units == "kg/ha")
Abundance_kg_ha <- dplyr::filter(Abundance_kg_ha, TreatmentType == "powder/granular")
Abundance_kg_ha_t2 <- dplyr::filter(Abundance_kg_ha, !is.na(AI.Rate_T2))
Abundance_kg_ha_t2$AI.Rate_T1 <- Abundance_kg_ha_t2$AI.Rate_T2
Abundance_kg_ha_t2$T1_Mean <- Abundance_kg_ha_t2$T2_Mean
Abundance_kg_ha_t2$T1_SE <- Abundance_kg_ha_t2$T2_SE
Abundance_kg_ha_t2$Study.T1..n. <- Abundance_kg_ha_t2$Study.T2..n.

Abundance_kg_ha <- rbind(Abundance_kg_ha, Abundance_kg_ha_t2)

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Abundance_kg_ha, vtype = "UB")

res7 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  AI.Rate_T1, slab = paste(dat1$Authors, dat1$Year))

#res2 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  T1_ppb +  factor(Functional.group), slab = paste(dat1$Authors, dat1$Year))
preds <- predict(res7, newmods = cbind(seq(from = min(dat1$AI.Rate_T1), to = max(dat1$AI.Rate_T1), length.out =  20)), addx = TRUE)
preds <- data.frame(pred = preds$pred, ci.lb = preds$ci.lb, ci.ub = preds$ci.ub, X.AI.Rate_T1 = preds$X[,2])

model7 <- data.frame(model = "y ~ Concentration[Kg/Ha]", p_value = res7$QMp, R_squared = round(res7$R2/100,2), AICc = res7$fit.stats$ML[5])
```

Despite that, the r squared of this model is `r round(res7$R2/100,2)`, that is over 40 percent of cariability explained by this factor alone. The relationship between concentration and Abundance can be seen in figure 4.


```{r, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.cap= "effect size of the Standardized mean difference of abundance and concentration (ppb)"}

ggplot(dat1, aes(x = AI.Rate_T1, y = yi))  + geom_ribbon(data = preds, aes(x = X.AI.Rate_T1, y = pred, ymin = ci.lb, ymax = ci.ub), fill = "grey", alpha = 0.5) + theme_classic() + geom_line(data = preds, aes(x = X.AI.Rate_T1, y = pred)) + geom_point() + xlab("Concentration (kg/ha)") + ylab("Standardized mean difference") + geom_hline(yintercept = 0, lty= 2)

```

### Abundance and concentration (g/Kg) for seed treatment

When we use concentration as parts per billion, the number of effect sizes diminishes from 101 to only nine.

```{r, message=FALSE, warning=FALSE, echo=FALSE}
Abundance <- dplyr::filter(Meta, Fitness.measure == "abundance")

Abundance_g_kg <- dplyr::filter(Abundance, Application.Units == "g/kg")


dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Abundance_g_kg, vtype = "UB")

res8 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  AI.Rate_T1, slab = paste(dat1$Authors, dat1$Year))

preds <- predict(res8, newmods = cbind(seq(from = min(dat1$AI.Rate_T1), to = max(dat1$AI.Rate_T1), length.out =  20)), addx = TRUE)
preds <- data.frame(pred = preds$pred, ci.lb = preds$ci.lb, ci.ub = preds$ci.ub, X.AI.Rate_T1 = preds$X[,2])

model8 <- data.frame(model = "y ~ Concentration[g/kg]", p_value = res8$QMp, R_squared = round(res8$R2/100,2), AICc = res8$fit.stats$ML[5])
```

Despite that, the r squared of this model is `r round(res8$R2/100,2)`, that is over 40 percent of cariability explained by this factor alone. The relationship between concentration and Abundance can be seen in figure 4.


```{r, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.cap= "effect size of the Standardized mean difference of abundance and concentration (ppb)"}

ggplot(dat1, aes(x = AI.Rate_T1, y = yi))  + geom_ribbon(data = preds, aes(x = X.AI.Rate_T1, y = pred, ymin = ci.lb, ymax = ci.ub), fill = "grey", alpha = 0.5) + theme_classic() + geom_line(data = preds, aes(x = X.AI.Rate_T1, y = pred)) + geom_point() + xlab("Concentration (g/kg)") + ylab("Standardized mean difference") + geom_hline(yintercept = 0, lty= 2)

```

### Abundance concentration and functional group

Again, when we have concentration, the number of studies is reduced form 101 to nine.

```{r, message=FALSE, warning=FALSE, echo=FALSE}
Abundance <- dplyr::filter(Meta, Fitness.measure == "abundance")
Abundance <- Abundance[!is.na(Abundance$T1_ppb),]

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Abundance, vtype = "UB")

res3 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  T1_ppb + factor(Functional.group), slab = paste(dat1$Authors, dat1$Year), test="knha")

library(caret)

newmods = expand.grid(T1_ppb = seq(from = min(dat1$T1_ppb), to = max(dat1$T1_ppb), length.out =  20), Functional.group = c("omnivore", "pollinator", "predator"))

dum <- dummyVars(~ Functional.group, data = newmods)

NM <- cbind(newmods[,1],predict(dum, newmods))

preds <- predict(res3, newmods = NM[,1:3])

preds <- data.frame(pred = preds$pred, ci.lb = preds$ci.lb, ci.ub = preds$ci.ub, T1_ppb = newmods$T1_ppb, Functional.group = newmods$Functional.group)

model3 <- data.frame(model = "y ~ Concentration + Functional group", p_value = res3$QMp, R_squared = round(res3$R2/100,2), AICc = res3$fit.stats$ML[5])
```

Adding functional group to the model increases R squared to `r round(res3$R2/100,2)`

```{r, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.cap= "effect size of the concentration and functional group on the  Standardized mean difference of abundance"}

ggplot(preds, aes(x = T1_ppb, y = pred))  + geom_ribbon(alpha = 0.5,aes(ymin = ci.lb, ymax = ci.ub, fill = Functional.group)) + theme_classic() + geom_line(aes(lty = Functional.group))+ xlab("Concentration (ppb)") + ylab("Standardized mean difference") + geom_hline(yintercept = 0, lty= 2) + scale_fill_grey()

```

### Abundance concentration and nesting area

```{r, message=FALSE, warning=FALSE, echo=FALSE}
Abundance <- dplyr::filter(Meta, Fitness.measure == "abundance")
Abundance <- Abundance[!is.na(Abundance$T1_ppb),]

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Abundance, vtype = "UB")

res5 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  T1_ppb + factor(Nesting.Area), slab = paste(dat1$Authors, dat1$Year), test="knha")



model5 <- data.frame(model = "y ~ Concentration + Nesting area", p_value = res5$QMp, R_squared = round(res5$R2/100,2), AICc = res5$fit.stats$ML[5])
```

### Full model

```{r, message=FALSE, warning=FALSE, echo=FALSE}
Abundance <- dplyr::filter(Meta, Fitness.measure == "abundance")
Abundance <- Abundance[!is.na(Abundance$T1_ppb),]

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Abundance, vtype = "UB")

res6 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  T1_ppb + factor(Nesting.Area) + factor(Functional.group), slab = paste(dat1$Authors, dat1$Year))



model6 <- data.frame(model = "y ~ Concentration + Nesting area + Functional group", p_value = res6$QMp, R_squared = round(res6$R2/100,2), AICc = res6$fit.stats$ML[5])
```

### Comparison of models

```{r, echo= FALSE}
All <- rbind(model0, model1, model2, model3, model4, model5, model6, model7, model8)

All <- dplyr::arrange(All, AICc)

All$deltaAICc <- (All$AICc - min(All$AICc))

knitr::kable(All, digits = 3, row.names = FALSE, caption = "Comparison of models taking into account p value, Pseudo R squared and AICc")
```

# Behaviour

### Behaviour and functional group

Using functional group as a moderator yields the following results

```{r, message=FALSE, warning=FALSE, echo=FALSE}
Behavior <- dplyr::filter(Meta, Fitness.measure == "behavior")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Behavior, vtype = "UB")

res <- rma(yi, vi, data=dat1, refline = 0, method = "HE", slab = paste(dat1$Authors, dat1$Year))

nullmod <- data.frame(estimate = res$b, ci.ub = res$ci.ub, ci.lb = res$ci.lb, group = c("Null"), p = res$pval, n =nrow(Behavior))



res0 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  factor(AI.type) - 1, slab = paste(dat1$Authors, dat1$Year))

AItype <- data.frame(estimate = res0$b, ci.ub = res0$ci.ub, ci.lb = res0$ci.lb, group = c("commercial","granular", "not specified", "seed treatment", "solution", "technical grade"), p = res0$pval, n = c(NROW(dplyr::filter(Behavior, AI.type == "commercial")), NROW(dplyr::filter(Behavior, AI.type == "granular")), NROW(dplyr::filter(Behavior, AI.type == "not specified")), NROW(dplyr::filter(Behavior, AI.type == "seed treatment")), NROW(dplyr::filter(Behavior, AI.type == "solution")), NROW(dplyr::filter(Behavior, AI.type == "technical grade"))))


All <- rbind(nullmod, AItype)

knitr::kable(All, digits = 3, row.names = FALSE, caption = "effect size of the Standardized mean difference of abundance for each functional group and it's standard error")

res1 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  factor(AI.type), slab = paste(dat1$Authors, dat1$Year))

model1 <- data.frame(model = "y ~ AI type", p_value = res1$QMp, R_squared = round(res1$R2/100,2), AICc = res1$fit.stats$ML[5])

```

the the psuedo R squared for this model was `r round(res1$R2/100,2)`, that is despite the mixed and omnivore funtional groups being statistically significant, functional group on its own does not explain the variability of the results very well.

```{r, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.cap= "effect size of the Standardized mean difference of behavior for each AI type and it's standard error"}

ggplot(All, aes(x = group, y = estimate)) + geom_point(aes(size = n)) + coord_flip() + geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub),width=0.0) + geom_hline(yintercept = 0, linetype=2) + ylim(c(-17, 17)) + ylab(c("Standardized Mean Difference")) + theme_classic() + xlab(c(""))

```

# Behavior and concentration (PPB)

When we use concentration as parts per billion, the number of effect sizes diminishes from 101 to only nine.

```{r, message=FALSE, warning=FALSE, echo=FALSE}
Behavior <- dplyr::filter(Meta, Fitness.measure == "behavior")
Behavior_ppb <- Behavior[!is.na(Behavior$T1_ppb),]

Behavior_ppb_t2 <- dplyr::filter(Behavior_ppb, !is.na(T2_ppb))
Behavior_ppb_t2$T1_ppb <- Behavior_ppb_t2$T2_ppb
Behavior_ppb_t2$T1_Mean <- Behavior_ppb_t2$T2_Mean
Behavior_ppb_t2$T1_SE <- Behavior_ppb_t2$T2_SE
Behavior_ppb_t2$Study.T1..n. <- Behavior_ppb_t2$Study.T2..n.

Behavior_ppb <- rbind(Behavior_ppb, Behavior_ppb_t2)

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Behavior_ppb, vtype = "UB")

res2 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  T1_ppb, slab = paste(dat1$Authors, dat1$Year))

#res2 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  T1_ppb +  factor(Functional.group), slab = paste(dat1$Authors, dat1$Year))
preds <- predict(res2, newmods = cbind(seq(from = min(dat1$T1_ppb), to = max(dat1$T1_ppb), length.out =  20)), addx = TRUE)
preds <- data.frame(pred = preds$pred, ci.lb = preds$ci.lb, ci.ub = preds$ci.ub, X.T1_ppb = preds$X[,2])

model2 <- data.frame(model = "y ~ Concentration", p_value = res2$QMp, R_squared = round(res2$R2/100,2), AICc = res2$fit.stats$ML[5])
```

Despite that, the r squared of this model is `r round(res2$R2/100,2)`, that is over 40 percent of cariability explained by this factor alone. The relationship between concentration and Abundance can be seen in figure 4.


```{r, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.cap= "effect size of the Standardized mean difference of behavior and concentration (ppb)"}

ggplot(dat1, aes(x = T1_ppb, y = yi))  + geom_ribbon(data = preds, aes(x = X.T1_ppb, y = pred, ymin = ci.lb, ymax = ci.ub), fill = "grey", alpha = 0.5) + theme_classic() + geom_line(data = preds, aes(x = X.T1_ppb, y = pred)) + geom_point(aes(size = Study.T1..n.)) + xlab("Concentration (ppb)") + ylab("Standardized mean difference") + geom_hline(yintercept = 0, lty= 2)

```

### Abundance concentration and functional group

Again, when we have concentration, the number of studies is reduced form 101 to nine.

```{r, message=FALSE, warning=FALSE, echo=FALSE}


Behavior <- dplyr::filter(Meta, Fitness.measure == "behavior")
Behavior_ppb <- Behavior[!is.na(Behavior$T1_ppb),]

Behavior_ppb_t2 <- dplyr::filter(Behavior_ppb, !is.na(T2_ppb))
Behavior_ppb_t2$T1_ppb <- Behavior_ppb_t2$T2_ppb
Behavior_ppb_t2$T1_Mean <- Behavior_ppb_t2$T2_Mean
Behavior_ppb_t2$T1_SE <- Behavior_ppb_t2$T2_SE
Behavior_ppb_t2$Study.T1..n. <- Behavior_ppb_t2$Study.T2..n.

Behavior_ppb <- rbind(Behavior_ppb, Behavior_ppb_t2)

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Behavior_ppb, vtype = "UB")


res3 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  T1_ppb + factor(Treatment.2), slab = paste(dat1$Authors, dat1$Year))

library(caret)

newmods = expand.grid(T1_ppb = seq(from = min(dat1$T1_ppb), to = max(dat1$T1_ppb), length.out =  20), Treatment.2 = c("CLO", "IMI"))

dum <- dummyVars(~ Treatment.2, data = newmods)

NM <- cbind(newmods[,1],predict(dum, newmods))

preds <- predict(res3, newmods = NM[,1:2])

preds <- data.frame(pred = preds$pred, ci.lb = preds$ci.lb, ci.ub = preds$ci.ub, T1_ppb = newmods$T1_ppb, Treatment.2 = newmods$Treatment.2)

model3 <- data.frame(model = "y ~ Concentration + neonic type", p_value = res3$QMp, R_squared = round(res3$R2/100,2), AICc = res3$fit.stats$ML[5])
```

Adding functional group to the model increases R squared to `r round(res3$R2/100,2)`

```{r, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.cap= "effect size of the concentration and neonic type on the behavior Standardized mean difference of abundance"}

ggplot(preds, aes(x = T1_ppb, y = pred))  + geom_ribbon(alpha = 0.5,aes(ymin = ci.lb, ymax = ci.ub, fill = Treatment.2)) + theme_classic() + geom_line(aes(lty = Treatment.2))+ xlab("Concentration (ppb)") + ylab("Standardized mean difference") + geom_hline(yintercept = 0, lty= 2) + scale_fill_grey() + geom_point(alpha = 0.8, data= dat1, aes(x = T1_ppb, y = yi, size = Study.T1..n., color = Treatment.2)) + scale_color_grey() + scale_x_log10()
```

### Comparison of models

```{r, echo= FALSE}
All <- rbind(model1, model2, model3)

All <- dplyr::arrange(All, AICc)

All$deltaAICc <- (All$AICc - min(All$AICc))

knitr::kable(All, digits = 3, row.names = FALSE, caption = "Comparison of models taking into account p value, Pseudo R squared and AICc")
```


Behavior/Reproduction and neonic AI (e.g., IMI, CLO) and ppb


Abundance

Seed treatment only 

AI type and functional group


Effects on:

Performance measures

Performance measures and functional group

Functional group

Performance measures and nesting area


Behavior

AI type and functional group


Reproduction and order and functional group

Abundance and order and functional group


Behavior and study type

Reproduction and nesting area


```{r, message=FALSE, warning=FALSE, echo=FALSE, fig.cap="test"}
ggplot(Meta, aes(x=reorder(Fitness.measure,Fitness.measure, function(x)-length(x)))) + geom_bar(aes(fill = Functional.group), position = "dodge")+ xlab("Performance measure") + ylab("Number of studies") + theme_classic() + scale_fill_grey()
```

References {#references .unnumbered}
==========
