---
title: Short Paper
author:
  - name: Anson Main
    email: maina@missouri.edu
    affiliation: School of Natural Resources
    footnote: Corresponding Author
  - name: Elisabeth Webb
    email: webbli@missouri.edu
    affiliation: School of Natural Resources
address:
  - code: Some Institute of Technology
    address: Department, Street, City, State, Zip
  - code: Another University
    address: Department, Street, City, State, Zip
abstract: |
  This is the abstract.

  It consists of two paragraphs.

bibliography: mybibfile.bib
output: rticles::elsevier_article
---

```{r, message=FALSE, warning=FALSE, echo=FALSE}
Meta <- readRDS("Meta2.rds")

library(ggplot2)
library(metafor)
```

# Methods

All analysis were carried away with the R Statistical Software [@Rcore], all meta-analyses were made on the metafor package [@viechtbauer2010conducting]. Our estimations were based on the use of random/mixed-effects models form of meta-analyses, which provide an unconditional inference about a larger set of studies from which the k studies included in the meta-analysis are assumed to be a random sample [@hedges1998fixed]. This estimations do not assume that this larger set consists only of studies that have actually been conducted, but instead envision a hypothetical population of studies that comprises studies that have been conducted, that could have been conducted, or that may be conducted in the future [@hedges1998fixed].

We used the *escalc* function of the metafor package to estimate the effect size estimates  [@viechtbauer2010conducting], we used the *standardized mean difference with heteroscedastic population variances in the two groups* (SDMH) as our estimator for effect size [@bonett2009meta], the metafor package also corrects the slight positive bias of the estimation following [@Wasserman1988]. To be extra conservative we used the unbiased estimates of the sampling variances. In all cases the residual heterogeneity estimator was Hedges. 

Since we used mixed effect models we used the The Knapp and Hartung adjustment **(Knapp and Hartung, 2003)** to  test the individual coefficients of the model. 

## Test for (Residual) Heterogeneity

For each model we tested for residual heterogeneity, if we used models without moderators, then the Cochran's Q-test [@cochran1954combination] was used to test whether the variability in the observed effect sizes or outcomes is larger than would be expected based on sampling variability alone. *A significant test suggests that the true effects or outcomes are heterogeneous*. When moderators were included in the models the Q_E-test for residual heterogeneity was used, this tests whether the variability in the observed effect sizes or outcomes not accounted for by the moderators included in the model is larger than would be expected based on sampling variability alone. When using moderators to explain more variability a pseudo R squared was computed following [@raudenbush2009analyzing].


# Results

As we can see in figure 1, the most common type of performance measured in studies was abundance, with 101 estimations, followed by reproduction with 44 estimation, behavior with 23, and finally survival and condition with 16 each.

```{r, message=FALSE, warning=FALSE, echo=FALSE, fig.cap= "Number of estimation of effect size within the meta-analyses"}

ggplot(Meta, aes(x=reorder(Fitness.measure,Fitness.measure, function(x)-length(x)))) + geom_bar() + xlab("Performance measure") + ylab("Number of studies") + theme_classic()
```

```{r, message=FALSE, warning=FALSE, echo=FALSE}

library(metafor)

#Abundance
Abundance <- dplyr::filter(Meta, Fitness.measure == "abundance")


dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Abundance, vtype = "UB")

res <- rma(yi, vi, data=dat1, refline = 0, method = "HE", slab = paste(dat1$Authors, dat1$Year))

Abund <- data.frame(estimate = res$b, ci.ub = res$ci.ub, ci.lb = res$ci.lb, group = c("Abundance"), p = res$pval, n =nrow(Abundance), I2= res$I2, pvalCT = res$QEp)
#Behavior

Behavior <- dplyr::filter(Meta, Fitness.measure == "behavior")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Behavior, vtype = "UB")

res2 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", slab = paste(dat1$Authors, dat1$Year))

Behav <- data.frame(estimate = res2$b, ci.ub = res2$ci.ub, ci.lb = res2$ci.lb, group = c("Behavior"), p = res2$pval, n =nrow(Behavior), I2= res2$I2, pvalCT = res2$QEp)
#Survival

survival <- dplyr::filter(Meta, Fitness.measure == "survival")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=survival, vtype = "UB")

res3 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", slab = paste(dat1$Authors, dat1$Year))

Surviv <- data.frame(estimate = res3$b, ci.ub = res3$ci.ub, ci.lb = res3$ci.lb, group = c("Survival"), p = res3$pval, n =nrow(survival), I2= res3$I2, pvalCT = res3$QEp)

#Reproduction

reproduction <- dplyr::filter(Meta, Fitness.measure == "reproduction")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=reproduction, vtype = "UB")

res4 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", slab = paste(dat1$Authors, dat1$Year))

Reprod <- data.frame(estimate = res4$b, ci.ub = res4$ci.ub, ci.lb = res4$ci.lb, group = c("Reproduction"), p = res4$pval, n =nrow(reproduction), I2= res4$I2, pvalCT = res4$QEp)

#Condition

condition <- dplyr::filter(Meta, Fitness.measure == "condition")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=condition, vtype = "UB")

res5 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", slab = paste(dat1$Authors, dat1$Year))

Cond <- data.frame(estimate = res5$b, ci.ub = res5$ci.ub, ci.lb = res5$ci.lb, group = c("Condition"), p = res5$pval, n =nrow(condition), I2= res5$I2, pvalCT = res5$QEp)

All <- rbind(Abund, Behav, Surviv, Reprod, Cond)
knitr::kable(All, digits = 3, row.names = FALSE, caption = "effect size of the Standardized mean difference for each type of estimation of performance, it's standard error and p-value")
```

## Overall effect size

As we can see in table 1 and figure 2, all estimations of the effects are negative. However, only abundance, survival and condition have significative negative effects. Survival has the highest effect size, with a mean difference estimation of `r round(Surviv$estimate,2)`


```{r, message=FALSE, warning=FALSE, echo=FALSE, fig.cap= "effect size of the Standardized mean difference for each type of estimation of performance and it's standard error"}
All <- All

ggplot(All, aes(x = group, y = estimate)) + geom_point(aes(size = n)) + coord_flip() + geom_errorbar(aes(ymin=ci.lb, ymax=ci.ub),width=0.0) + geom_hline(yintercept = 0, linetype=2) + ylim(c(-15, 15)) + ylab(c("Standardized Mean Difference")) + theme_classic() + xlab(c(""))

```

# Estimations using moderators:

### Abundance models without concentrations 


```{r, message=FALSE, warning=FALSE, echo=FALSE}
Abundance <- dplyr::filter(Meta, Fitness.measure == "abundance")

#### Names
Cols <- c("Order", "Functional group", "Treatment Type", "Neonic", "Nesting Area")
n <- length(Cols)

id <- unlist(
  lapply(1:n,
         function(i)combn(1:n,i,simplify=FALSE)
  )
  ,recursive=FALSE)

ModelNames <- sapply(id,function(i)
  paste("y~",paste(Cols[i],collapse="+"))
)


dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Abundance, vtype = "UB")

Cols <- c("factor(Order)", "factor(Functional.group)", "factor(TreatmentType)", "factor(Treatment.2)", "factor(Nesting.Area)")
n <- length(Cols)

id <- unlist(
  lapply(1:n,
         function(i)combn(1:n,i,simplify=FALSE)
  )
  ,recursive=FALSE)

Formulas <- sapply(id,function(i)
  paste("~",paste(Cols[i],collapse="+"))
)

resabund <- lapply(Formulas,function(i)
  rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =as.formula(i), slab = paste(dat1$Authors, dat1$Year))
)
res1 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  factor(Functional.group), slab = paste(dat1$Authors, dat1$Year))

modelAbund <- data.frame(model = character(length(resabund)), pvalue = numeric(length(resabund)), R_squared = numeric(length(resabund)), n = numeric(length(resabund)), AICc = numeric(length(resabund)), stringsAsFactors = FALSE)

for (i in 1:length(resabund)){
  modelAbund[i,1]<- ModelNames[i]
  modelAbund[i,2]<- resabund[[i]]$QMp
  modelAbund[i,3]<- round(resabund[[i]]$R2/100,2)
  modelAbund[i,4]<- NROW(dat1)
  modelAbund[i,5]<- resabund[[i]]$fit.stats$ML[5]
}
```

### Comparison of models without concentrations

```{r, echo= FALSE}
modelAbund <- dplyr::arrange(modelAbund, AICc)

modelAbund$deltaAICc <- (modelAbund$AICc - min(modelAbund$AICc))

SUMDELTA <- sum(exp(-0.5*modelAbund$deltaAICc))

modelAbund$Weight <- exp(-0.5*modelAbund$deltaAICc)/SUMDELTA

modelAbund <- dplyr::filter(modelAbund, deltaAICc < 5)

knitr::kable(modelAbund, digits = 3, row.names = FALSE, caption = "Comparison of models taking into account p value, Pseudo R squared and AICc")
```

### Abundance and concentration (Kg/Ha) for Powder/granular treatment models 


```{r, message=FALSE, warning=FALSE, echo=FALSE}
Abundance <- dplyr::filter(Meta, Fitness.measure == "abundance")

Abundance_kg_ha <- dplyr::filter(Abundance, Application.Units == "kg/ha")
Abundance_kg_ha <- dplyr::filter(Abundance_kg_ha, TreatmentType == "powder/granular")

#### Names
Cols <- c("Order", "Functional group", "Nesting Area", "Concentration [Kg/Ha]")
n <- length(Cols)

id <- unlist(
  lapply(1:n,
         function(i)combn(1:n,i,simplify=FALSE)
  )
  ,recursive=FALSE)

ModelNames <- sapply(id,function(i)
  paste("y~",paste(Cols[i],collapse="+"))
)

ModelNames<-ModelNames[grep("Conc", ModelNames)]

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Abundance_kg_ha, vtype = "UB")

Cols <- c("factor(Order)", "factor(Functional.group)", "factor(Nesting.Area)", "AI.Rate_T1")
n <- length(Cols)

id <- unlist(
  lapply(1:n,
         function(i)combn(1:n,i,simplify=FALSE)
  )
  ,recursive=FALSE)

Formulas <- sapply(id,function(i)
  paste("~",paste(Cols[i],collapse="+"))
)

Formulas <- Formulas[grep("AI.Rate_T1", Formulas)]


resabund <- lapply(Formulas,function(i)
  rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =as.formula(i), slab = paste(dat1$Authors, dat1$Year))
)
res1 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  factor(Functional.group), slab = paste(dat1$Authors, dat1$Year))

modelAbund <- data.frame(model = character(length(resabund)), pvalue = numeric(length(resabund)), R_squared = numeric(length(resabund)), n = numeric(length(resabund)), AICc = numeric(length(resabund)), stringsAsFactors = FALSE)

for (i in 1:length(resabund)){
  modelAbund[i,1]<- ModelNames[i]
  modelAbund[i,2]<- resabund[[i]]$QMp
  modelAbund[i,3]<- round(resabund[[i]]$R2/100,2)
  modelAbund[i,4]<- NROW(dat1)
  modelAbund[i,5]<- resabund[[i]]$fit.stats$ML[5]
}
```

```{r, message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.cap= "effect size of the Standardized mean difference of behavior and concentration (Kg/Ha) for powder/granular aplications"}

#ggplot(dat1, aes(x = AI.Rate_T1, y = yi))  + geom_ribbon(data = preds, aes(x = X.AI.Rate_T1, y = pred, ymin = ci.lb, ymax = ci.ub), fill = "grey", alpha = 0.5) + theme_classic() + geom_line(data = preds, aes(x = X.AI.Rate_T1, y = pred)) + geom_point() + xlab("Concentration (Kg/Ha)") + ylab("Standardized mean difference") + geom_hline(yintercept = 0, lty= 2) + scale_size("Number of studies") + scale_x_continuous(labels = scales::comma)

```


### Comparison of models with concentrations [Kg/Ha]

```{r, echo= FALSE}
modelAbund <- dplyr::arrange(modelAbund, AICc)

modelAbund$deltaAICc <- (modelAbund$AICc - min(modelAbund$AICc))

SUMDELTA <- sum(exp(-0.5*modelAbund$deltaAICc))

modelAbund$Weight <- exp(-0.5*modelAbund$deltaAICc)/SUMDELTA

modelAbund <- dplyr::filter(modelAbund, deltaAICc < 5)

knitr::kable(modelAbund, digits = 3, row.names = FALSE, caption = "Comparison of models taking into account p value, Pseudo R squared and AICc")
```

### Abundance and concentration (g/Kg) models with seed treatment

```{r, message=FALSE, warning=FALSE, echo=FALSE}

Abundance <- dplyr::filter(Meta, Fitness.measure == "abundance")

Abundance_g_kg <- dplyr::filter(Abundance, Application.Units == "g/kg")


dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Abundance_g_kg, vtype = "UB")

Cols <- c("Order", "Functional group", "Nesting Area", "Concentration [g/Kg]")
n <- length(Cols)

id <- unlist(
  lapply(1:n,
         function(i)combn(1:n,i,simplify=FALSE)
  )
  ,recursive=FALSE)

ModelNames <- sapply(id,function(i)
  paste("y~",paste(Cols[i],collapse="+"))
)

ModelNames<-ModelNames[grep("Conc", ModelNames)]

Cols <- c("factor(Order)", "factor(Functional.group)", "factor(Nesting.Area)", "AI.Rate_T1")
n <- length(Cols)

id <- unlist(
  lapply(1:n,
         function(i)combn(1:n,i,simplify=FALSE)
  )
  ,recursive=FALSE)

Formulas <- sapply(id,function(i)
  paste("~",paste(Cols[i],collapse="+"))
)

Formulas <- Formulas[grep("AI.Rate_T1", Formulas)]

resabund <- lapply(Formulas,function(i)
  rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =as.formula(i), slab = paste(dat1$Authors, dat1$Year))
)
res1 <- rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =~  factor(Functional.group), slab = paste(dat1$Authors, dat1$Year))

modelAbund <- data.frame(model = character(length(resabund)), pvalue = numeric(length(resabund)), R_squared = numeric(length(resabund)), n = numeric(length(resabund)), AICc = numeric(length(resabund)), stringsAsFactors = FALSE)

for (i in 1:length(resabund)){
  modelAbund[i,1]<- ModelNames[i]
  modelAbund[i,2]<- resabund[[i]]$QMp
  modelAbund[i,3]<- round(resabund[[i]]$R2/100,2)
  modelAbund[i,4]<- NROW(dat1)
  modelAbund[i,5]<- resabund[[i]]$fit.stats$ML[5]
}

```


### Comparison of models [g/Kg]

```{r, echo= FALSE}
modelAbund <- dplyr::arrange(modelAbund, AICc)

modelAbund$deltaAICc <- (modelAbund$AICc - min(modelAbund$AICc))

SUMDELTA <- sum(exp(-0.5*modelAbund$deltaAICc))

modelAbund$Weight <- exp(-0.5*modelAbund$deltaAICc)/SUMDELTA

modelAbund <- dplyr::filter(modelAbund, deltaAICc < 5)


knitr::kable(modelAbund, digits = 3, row.names = FALSE, caption = "Comparison of models taking into account p value, Pseudo R squared and AICc")
```



# Behaviour

###Behaviour without concentration

```{r, message=FALSE, warning=FALSE, echo=FALSE}
### Behaviour and AI type

Behavior <- dplyr::filter(Meta, Fitness.measure == "behavior")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Behavior, vtype = "UB")

Cols <- c("Order", "Functional group", "Nesting Area", "Neonic", "Treatment Type", "Study Type")


n <- length(Cols)

id <- unlist(
  lapply(1:n,
         function(i)combn(1:n,i,simplify=FALSE)
  )
  ,recursive=FALSE)

ModelNames <- sapply(id,function(i)
  paste("y~",paste(Cols[i],collapse="+"))
)


Cols <- c("factor(Order)", "factor(Functional.group)", "factor(Nesting.Area)", "factor(Treatment.2)", "factor(TreatmentType)", "factor(Study.Type)")
n <- length(Cols)

id <- unlist(
  lapply(1:n,
         function(i)combn(1:n,i,simplify=FALSE)
  )
  ,recursive=FALSE)

Formulas <- sapply(id,function(i)
  paste("~",paste(Cols[i],collapse="+"))
)

resbehav <- lapply(Formulas,function(i)
  rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =as.formula(i), slab = paste(dat1$Authors, dat1$Year))
)


modelBehav <- data.frame(model = character(length(resbehav)), pvalue = numeric(length(resbehav)), R_squared = numeric(length(resbehav)), n = numeric(length(resbehav)), AICc = numeric(length(resbehav)), stringsAsFactors = FALSE)

for (i in 1:length(resbehav)){
  modelBehav[i,1]<- ModelNames[i]
  modelBehav[i,2]<- resbehav[[i]]$QMp
  modelBehav[i,3]<- round(resbehav[[i]]$R2/100,2)
  modelBehav[i,4]<- NROW(dat1)
  modelBehav[i,5]<- resbehav[[i]]$fit.stats$ML[5]
}

```


###Model Comparison behaviour without concentration

```{r, echo= FALSE}
modelBehav <- dplyr::arrange(modelBehav, AICc)

modelBehav$deltaAICc <- (modelBehav$AICc - min(modelBehav$AICc))

SUMDELTA <- sum(exp(-0.5*modelBehav$deltaAICc))

modelBehav$Weight <- exp(-0.5*modelBehav$deltaAICc)/SUMDELTA

modelBehav <- dplyr::filter(modelBehav, deltaAICc < 5)

knitr::kable(modelBehav, digits = 3, row.names = FALSE, caption = "Comparison of models taking into account p value, Pseudo R squared and AICc")
```


#Reproduction

###Reproduction without concentration

```{r, message=FALSE, warning=FALSE, echo=FALSE}
### Reproduction, functional group and Order

Reproduction <- dplyr::filter(Meta, Fitness.measure == "reproduction")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Reproduction, vtype = "UB")


Cols <- c("Order", "Functional group", "Nesting Area", "Neonic", "Treatment Type", "Study Type")


n <- length(Cols)

id <- unlist(
  lapply(1:n,
         function(i)combn(1:n,i,simplify=FALSE)
  )
  ,recursive=FALSE)

ModelNames <- sapply(id,function(i)
  paste("y~",paste(Cols[i],collapse="+"))
)


Cols <- c("factor(Order)", "factor(Functional.group)", "factor(Nesting.Area)", "factor(Treatment.2)", "factor(TreatmentType)", "factor(Study.Type)")
n <- length(Cols)

id <- unlist(
  lapply(1:n,
         function(i)combn(1:n,i,simplify=FALSE)
  )
  ,recursive=FALSE)

Formulas <- sapply(id,function(i)
  paste("~",paste(Cols[i],collapse="+"))
)

resrepro <- lapply(Formulas,function(i)
  rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =as.formula(i), slab = paste(dat1$Authors, dat1$Year))
)


modelRepro <- data.frame(model = character(length(resrepro)), pvalue = numeric(length(resrepro)), R_squared = numeric(length(resrepro)), n = numeric(length(resrepro)), AICc = numeric(length(resrepro)), stringsAsFactors = FALSE)

for (i in 1:length(resrepro)){
  modelRepro[i,1]<- ModelNames[i]
  modelRepro[i,2]<- resrepro[[i]]$QMp
  modelRepro[i,3]<- round(resrepro[[i]]$R2/100,2)
  modelRepro[i,4]<- NROW(dat1)
  modelRepro[i,5]<- resrepro[[i]]$fit.stats$ML[5]
}

```


###Model Comparison reproduction without concentration

```{r, echo= FALSE}
modelRepro <- dplyr::arrange(modelRepro, AICc)

modelRepro$deltaAICc <- (modelRepro$AICc - min(modelRepro$AICc))

SUMDELTA <- sum(exp(-0.5*modelRepro$deltaAICc))

modelRepro$Weight <- exp(-0.5*modelRepro$deltaAICc)/SUMDELTA

modelRepro <- dplyr::filter(modelRepro, deltaAICc < 5)

knitr::kable(modelRepro, digits = 3, row.names = FALSE, caption = "Comparison of models taking into account p value, Pseudo R squared and AICc")
```

###Reproduction and concentration [ppb]

```{r, message=FALSE, warning=FALSE, echo=FALSE}
#Reproduction and ppb
Reproduction <- dplyr::filter(Meta, Fitness.measure == "reproduction")
Reproduction_ppb <- Reproduction[!is.na(Reproduction$T1_ppb),]

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=Reproduction_ppb, vtype = "UB")


Cols <- c("Order", "Functional group", "Nesting Area", "Neonic", "Treatment Type", "Study Type", "Concentration [ppb]")


n <- length(Cols)

id <- unlist(
  lapply(1:n,
         function(i)combn(1:n,i,simplify=FALSE)
  )
  ,recursive=FALSE)

ModelNames <- sapply(id,function(i)
  paste("y~",paste(Cols[i],collapse="+"))
)

ModelNames <- ModelNames[grep("Conc", ModelNames)]

Cols <- c("factor(Order)", "factor(Functional.group)", "factor(Nesting.Area)", "factor(Treatment.2)", "factor(TreatmentType)", "factor(Study.Type)", "T1_ppb")
n <- length(Cols)

id <- unlist(
  lapply(1:n,
         function(i)combn(1:n,i,simplify=FALSE)
  )
  ,recursive=FALSE)

Formulas <- sapply(id,function(i)
  paste("~",paste(Cols[i],collapse="+"))
)

Formulas <- Formulas[grep("T1_ppb", Formulas)]


resrepro <- lapply(Formulas,function(i)
  rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =as.formula(i), slab = paste(dat1$Authors, dat1$Year))
)


modelRepro <- data.frame(model = character(length(resrepro)), pvalue = numeric(length(resrepro)), R_squared = numeric(length(resrepro)), n = numeric(length(resrepro)), AICc = numeric(length(resrepro)), stringsAsFactors = FALSE)

for (i in 1:length(resrepro)){
  modelRepro[i,1]<- ModelNames[i]
  modelRepro[i,2]<- resrepro[[i]]$QMp
  modelRepro[i,3]<- round(resrepro[[i]]$R2/100,2)
  modelRepro[i,4]<- NROW(dat1)
  modelRepro[i,5]<- resrepro[[i]]$fit.stats$ML[5]
}

```


###Model Comparison reproduction with concentration [ppb]

```{r, echo= FALSE}
modelRepro <- dplyr::arrange(modelRepro, AICc)

modelRepro$deltaAICc <- (modelRepro$AICc - min(modelRepro$AICc))

SUMDELTA <- sum(exp(-0.5*modelRepro$deltaAICc))

modelRepro$Weight <- exp(-0.5*modelRepro$deltaAICc)/SUMDELTA

modelRepro <- dplyr::filter(modelRepro, deltaAICc < 5)

knitr::kable(modelRepro, digits = 3, row.names = FALSE, caption = "Comparison of models taking into account p value, Pseudo R squared and AICc")

write.csv(modelRepro, "model_repro.csv")
```

# Condition

```{r, message=FALSE, warning=FALSE, echo=FALSE}
### Reproduction, functional group and Order
condition <- dplyr::filter(Meta, Fitness.measure == "condition")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=condition, vtype = "UB")


Cols <- c("Order", "Functional group", "Nesting Area", "Neonic", "Treatment Type", "Study Type")


n <- length(Cols)

id <- unlist(
  lapply(1:n,
         function(i)combn(1:n,i,simplify=FALSE)
  )
  ,recursive=FALSE)

ModelNames <- sapply(id,function(i)
  paste("y~",paste(Cols[i],collapse="+"))
)


Cols <- c("factor(Order)", "factor(Functional.group)", "factor(Nesting.Area)", "factor(Treatment.2)", "factor(TreatmentType)", "factor(Study.Type)")
n <- length(Cols)

id <- unlist(
  lapply(1:n,
         function(i)combn(1:n,i,simplify=FALSE)
  )
  ,recursive=FALSE)

Formulas <- sapply(id,function(i)
  paste("~",paste(Cols[i],collapse="+"))
)

rescondition <- lapply(Formulas,function(i)
  rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =as.formula(i), slab = paste(dat1$Authors, dat1$Year))
)


modelCond <- data.frame(model = character(length(rescondition)), pvalue = numeric(length(rescondition)), R_squared = numeric(length(rescondition)), n = numeric(length(rescondition)), AICc = numeric(length(rescondition)), stringsAsFactors = FALSE)

for (i in 1:length(rescondition)){
  modelCond[i,1]<- ModelNames[i]
  modelCond[i,2]<- rescondition[[i]]$QMp
  modelCond[i,3]<- round(rescondition[[i]]$R2/100,2)
  modelCond[i,4]<- NROW(dat1)
  modelCond[i,5]<- rescondition[[i]]$fit.stats$ML[5]
}

```


###Model Comparison reproduction without concentration

```{r, echo= FALSE}
modelCond <- dplyr::arrange(modelCond, AICc)

modelCond$deltaAICc <- (modelCond$AICc - min(modelCond$AICc))

SUMDELTA <- sum(exp(-0.5*modelCond$deltaAICc))

modelCond$Weight <- exp(-0.5*modelCond$deltaAICc)/SUMDELTA

modelCond <- dplyr::filter(modelCond, deltaAICc < 5)

knitr::kable(modelCond, digits = 3, row.names = FALSE, caption = "Comparison of models taking into account p value, Pseudo R squared and AICc")
```

## Condtion with concetration [ppb]

```{r, message=FALSE, warning=FALSE, echo=FALSE}
### Reproduction, functional group and Order
condition <- dplyr::filter(Meta, Fitness.measure == "condition")
condition_ppb <- condition[!is.na(condition$T1_ppb),]


dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=condition_ppb, vtype = "UB")


Cols <- c("Order", "Functional group", "Nesting Area", "Neonic", "Study Type", "Concentration [ppb]")


n <- length(Cols)

id <- unlist(
  lapply(1:n,
         function(i)combn(1:n,i,simplify=FALSE)
  )
  ,recursive=FALSE)

ModelNames <- sapply(id,function(i)
  paste("y~",paste(Cols[i],collapse="+"))
)

ModelNames <- ModelNames[grep("Conc", ModelNames)]


Cols <- c("factor(Order)", "factor(Functional.group)", "factor(Nesting.Area)", "factor(Treatment.2)", "factor(Study.Type)", "T1_ppb")
n <- length(Cols)

id <- unlist(
  lapply(1:n,
         function(i)combn(1:n,i,simplify=FALSE)
  )
  ,recursive=FALSE)

Formulas <- sapply(id,function(i)
  paste("~",paste(Cols[i],collapse="+"))
)

Formulas <- Formulas[grep("T1_ppb", Formulas)]


rescondition <- lapply(Formulas,function(i)
  rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =as.formula(i), slab = paste(dat1$Authors, dat1$Year))
)


modelCond <- data.frame(model = character(length(rescondition)), pvalue = numeric(length(rescondition)), R_squared = numeric(length(rescondition)), n = numeric(length(rescondition)), AICc = numeric(length(rescondition)), stringsAsFactors = FALSE)

for (i in 1:length(rescondition)){
  modelCond[i,1]<- ModelNames[i]
  modelCond[i,2]<- rescondition[[i]]$QMp
  modelCond[i,3]<- round(rescondition[[i]]$R2/100,2)
  modelCond[i,4]<- NROW(dat1)
  modelCond[i,5]<- rescondition[[i]]$fit.stats$ML[5]
}

```


###Model Comparison reproduction with concentration ppb

```{r, echo= FALSE, results='asis'}
modelCond <- dplyr::arrange(modelCond, AICc)

modelCond$deltaAICc <- (modelCond$AICc - min(modelCond$AICc))

SUMDELTA <- sum(exp(-0.5*modelCond$deltaAICc))

modelCond$Weight <- exp(-0.5*modelCond$deltaAICc)/SUMDELTA

modelCond <- dplyr::filter(modelCond, deltaAICc < 5)

knitr::kable(modelCond, digits = 3, row.names = FALSE, caption = "Comparison of models taking into account p value, Pseudo R squared and AICc")
```

# Survival


```{r, message=FALSE, warning=FALSE, echo=FALSE}
### Reproduction, functional group and Order
survival <- dplyr::filter(Meta, Fitness.measure == "survival")

dat1 <- escalc(measure="SMDH", m2i=Con_Mean, sd2i=Con_SE, n2i=Study.control..n., m1i=T1_Mean, sd1i=T1_SE, n1i=Study.T1..n., data=survival, vtype = "UB")


Cols <- c("Order", "Functional group", "Nesting Area", "Neonic", "Treatment Type", "Study Type")


n <- length(Cols)

id <- unlist(
  lapply(1:n,
         function(i)combn(1:n,i,simplify=FALSE)
  )
  ,recursive=FALSE)

ModelNames <- sapply(id,function(i)
  paste("y~",paste(Cols[i],collapse="+"))
)


Cols <- c("factor(Order)", "factor(Functional.group)", "factor(Nesting.Area)", "factor(Treatment.2)", "factor(TreatmentType)", "factor(Study.Type)")
n <- length(Cols)

id <- unlist(
  lapply(1:n,
         function(i)combn(1:n,i,simplify=FALSE)
  )
  ,recursive=FALSE)

Formulas <- sapply(id,function(i)
  paste("~",paste(Cols[i],collapse="+"))
)

resSurvival <- lapply(Formulas,function(i)
  rma(yi, vi, data=dat1, refline = 0, method = "HE", mods =as.formula(i), slab = paste(dat1$Authors, dat1$Year))
)


ModelSurv <- data.frame(model = character(length(resSurvival)), pvalue = numeric(length(resSurvival)), R_squared = numeric(length(resSurvival)), n = numeric(length(resSurvival)), AICc = numeric(length(resSurvival)), stringsAsFactors = FALSE)

for (i in 1:length(resSurvival)){
  ModelSurv[i,1]<- ModelNames[i]
  ModelSurv[i,2]<- resSurvival[[i]]$QMp
  ModelSurv[i,3]<- round(resSurvival[[i]]$R2/100,2)
  ModelSurv[i,4]<- NROW(dat1)
  ModelSurv[i,5]<- resSurvival[[i]]$fit.stats$ML[5]
}

resSurvival[[5]]
unique(dat1$TreatmentType)
```


###Model Comparison Survival without concentration

```{r, echo= FALSE}
ModelSurv <- dplyr::arrange(ModelSurv, AICc)

ModelSurv$deltaAICc <- (ModelSurv$AICc - min(ModelSurv$AICc))

SUMDELTA <- sum(exp(-0.5*ModelSurv$deltaAICc))

ModelSurv$Weight <- exp(-0.5*ModelSurv$deltaAICc)/SUMDELTA

ModelSurv <- dplyr::filter(ModelSurv, deltaAICc < 5)

knitr::kable(ModelSurv, digits = 3, row.names = FALSE, caption = "Comparison of models taking into account p value, Pseudo R squared and AICc")
```

References {#references .unnumbered}
==========
